Titeltext

### 2018-07-25 thesis/paper/paper.tex
Added conflicts-with

\newpage
\subsection{Item requires statement (Q21503247)}\label{subsec_item_requires_statement}
The item requires statement constraint requires an additional statement on an item with a statement using the constrained property, possibly also using a specific value from the list of allowed values.
\begin{table}[H]
\caption{item requires statement constraint (Q21503247)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & item statement \\
\hline
Qualifiers & \makecell{required property (P2306) -- 1 \\ property the item statement must have \\ allowed value (P2305) -- 0..* \\ values the item statement may have} \\
\hline
Violation & \makecell{no item statement with required property \\ all item statements with required property have no allowed value} \\
\hline
Dependency &  all statements of a constrained item\\
\hline
Rule features & negation \\
\hline
\end{tabularx}
\end{table}

@@

>>>>

\newpage
\subsection{Item requires statement (Q21503247)}\label{subsec_item_requires_statement}
The item requires statement constraint requires an additional statement on an item with a statement using the constrained property, possibly also using a specific value from the list of allowed values.
\begin{table}[H]
\caption{item requires statement constraint (Q21503247)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & item statement \\
\hline
Qualifiers & \makecell{required property (P2306) -- 1 \\ property the item statement must have \\ allowed value (P2305) -- 0..* \\ values the item statement may have} \\
\hline
Violation & \makecell{no item statement with required property \\ all item statements with required property have no allowed value} \\
\hline
Dependency &  all item statements\\
\hline
Rule features & negation \\
\hline
\end{tabularx}
\end{table}

@@

\subsection{Conflicts-with (Q21502838)}
The conflicts with constraint forbids either certain statements or statements with a specific property on constrained items.
\begin{table}[H]
\caption{Conflicts-with constraint (Q21502838)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & item statement \\
\hline
Qualifiers & \makecell{conflicting property (P2306) -- 1 \\ property no item statement may have (with conflicting values if specified) \\
conflicting values (P2305) -- 0..* \\ values that may not appear in item statements with the conflicting property} \\
\hline
Violation & \makecell{item statement with the conflicting property \\ item statement with the conflicting property and one of the conflicting values} \\
\hline
Dependency & all item statements \\
\hline
\end{tabularx}
\end{table}
The rule modelling can simply be done by choosing all tripleEDB with the constrained property and then all tripleEDB on the same item with the conflicting property, specifying the values as well if necessary.
